A Wait-free Queue with Polylogarithmic Step Complexity

### 2023-05-12 podc_paper/correctness.tex
minor fixes
Edited for camera-ready version:  changed references to appendix to arxiv version

The accuracy of the values stored in the \fld{sum\sub{enq}} and \fld{sum\sub{deq}} fields
on lines \ref{enqNew}, \ref{deqNew}, \ref{createSumEnq} and \ref{createSumDeq} follows easily
from the definition of subblocks.  See Appendix 
\ref{app::tracingDetails} for a detailed proof of \Cref{lem::sum}.

@@

Next, we show two \op{Refresh}es suffice to propagate operations from a child to its parent.
We say that node $\var{v}$ \emph{contains} an operation $op$ if some block in $\var{v}.\fld{blocks}$ contains $op$.
%\here{move this defn earlier and just recall it here?}
Since blocks are permanently added to nodes, if $\var{v}$ contains $op$ at some time, $v$ contains $op$ at all later times too.

@@

See Appendix \ref{app::tracingDetails} for detailed proofs for this section.

@@

A simple proof (in Appendix \ref{app::tracingDetails}) shows that \fld{size} fields are computed correctly.
\begin{restatable}{lemma}{sizeCorrectRes}
\label{sizeCorrectness}
If the operations of $\var{root}.\fld{blocks}[0..b]$ are applied sequentially in the order of~$L$ on an initially empty queue, the resulting queue has $\var{root}.\fld{blocks}[b].\size$ elements.  
\end{restatable}

>>>>

The accuracy of the values stored in the \fld{sum\sub{enq}} and \fld{sum\sub{deq}} fields
on lines \ref{enqNew}, \ref{deqNew}, \ref{createSumEnq} and \ref{createSumDeq} follows easily
from the definition of subblocks.  See 
%Appendix \ref{app::tracingDetails} 
the full version \cite{full} for a detailed proof of \Cref{lem::sum}.

@@

In the next two lemmas, we show two \op{Refresh}es suffice to propagate operations from a child to its parent.
We say that node $\var{v}$ \emph{contains} an operation $op$ if some block in $\var{v}.\fld{blocks}$ contains $op$.
%\here{move this defn earlier and just recall it here?}
Since blocks are permanently added to nodes, if $\var{v}$ contains $op$ at some time, $v$ contains $op$ at all later times too.

@@

See 
%Appendix \ref{app::tracingDetails}
the full version \cite{full} for detailed proofs for this section.

@@

A simple proof (in 
%Appendix \ref{app::tracingDetails})
the full version \cite{full})
shows that \fld{size} fields are computed correctly.
\begin{restatable}{lemma}{sizeCorrectRes}
\label{sizeCorrectness}
If the operations of $\var{root}.\fld{blocks}[0..b]$ are applied sequentially in the order of~$L$ on an initially empty queue, the resulting queue has $\var{root}.\fld{blocks}[b].\size$ elements.  
\end{restatable}
